NFC and burnout in teachers - A replication and extension study

### 2022-07-29 Manuscript/Revision_Letter.Rmd
added anonymous link
implemented Anjas comments

Thank you for this suggestion.
Our intention was not to focus on the significant mediations of Grass et al. (2018), but to deepen the understanding of the role of NFC in burnout.
Therefore, we focussed on RPE, because it is likely the most relevant subscale of the MBI scale in the context of NFC (as Grass et al. also argued).
While Grass et al. (2018) did not find significant correlations between NFC and the subscales DP and EE, Naderi et al. (2018, http://saber.ucv.ve/ojs/index.php/rev_lh/article/view/15958) showed that in students, NFC was significantly correlated with DP and EE, but less so than with RPE.
It has been shown that NFC is positively associated with higher self-efficacy (Rooij et al. (2017), https://doi.org/10.1080/13596748.2017.1381301, and Tan et al. (2020), https://doi.org/10.1007/s12528-019-09239-6), so we also expected NFC to be more strongly associated with the RPE subscale than with DP or EE.
And if the focus in burnout studies with teacher samples has been on the DP and EE subscales, it is all the more reason to also focus on the RPE subscale, especially because NFC was equally correlated with all MBI subscales in our teacher sample.
We had preregistered the exploratory analysis of the Demand-Resource-Ratio model with RPE in place of the MBI score, but this model did not have better fit indices than the initial model, which might be attributed to the evenly distributed associations between NFC and the subscales.
Furthermore, when constructing the exploratory model it became clear that NFC was indeed associated with RPE and EE via DRF and DTH, respectively, but the DP subscale did not have any meaningful paths within the model.
Since we have not preregistered any analysis of the association between NFC and DP or EE, and we do not have any theory-driven hypotheses regarding these associations, we do not believe that such analyses would contribute to the goals of the paper.
A change that we will gladly implement is the more specific distinction between the terms "burnout" and "RPE subscale" in the manuscript, thank you for this advice.

@@

We do not agree that this item justifies claims for a confounding of Covid burden and years of experience.
Firstly, years of experience cannot be equated with age, as some teachers are lateral entry employees.
Secondly, age itself is not the only risk factor for Covid, but one of a long list of risk factors according to the Center for Disease Control and Prevention, such as disability, asthma, cancer, chronic heart disease, diabetes, HIV, weak immune function, obesity, mental disorders, pregnancy, physical inactivity, etc.
Since the item does not specify the kind of risk factor, there is no need to correct for any confound between Covid burden and years of experience.

@@

Thank you for this assessment.
It is true that the theoretical framework shifts within the manuscript, but this is absolutely intentional.
We wanted to use one data set to investigate multiple aims that each have a right to exist but are not "long" enough for papers of their own.
And as the investigation of demands and resources in the context of Need for Cognition is very new, a smaller confirmatory model and a larger exploratory model likely contribute more to developing this approach than a highly complex and long paper with a theoretical framework that is still in its infancy.
The overarching framework in this manuscript is the role of Need for Cognition in burnout or burnout subscales, and depending on which specific aim the reader is interested in, they may skim over the others.
We have added subheadings to the introduction and expanded the last paragraph before the methods section to better convey these three aims:

@@

We are aware that the double-blind review process somewhat interferes with Open Science issues.
We learned how OSF projects can be anonymized only after submission of our manuscript.
We apologize that we did not give the reviewer the opportunity to check our preregistration/data/code.
Of course, we share our data and code openly on OSF and also provide a license for re-use (CC-4.0-BY).

@@

Thank you for this suggestion.
The three-part-structure was exactly what we intended with this manuscript; a replication in a different sample, an analysis based on our own previous research, and an exploratory analysis to serve as a starting point for future research.
Each part is relevant but not "long enough" to warrant its own paper.
(As we have provided an answer to this issue in our response to your first comment, we would kindly refer to it here.)

>>>>

Thank you for this suggestion.
Our intention was not to focus on the significant mediations of Grass et al. (2018), but to deepen the understanding of the role of NFC in burnout.
Therefore, we focussed on RPE, because it is likely the most relevant subscale of the MBI scale in the context of NFC (as Grass et al. also argued).
While Grass et al. (2018) did not find significant correlations between NFC and the subscales DP and EE, Naderi et al. (2018, http://saber.ucv.ve/ojs/index.php/rev_lh/article/view/15958) showed that in students, NFC was significantly correlated with DP and EE, but less so than with RPE.
It has been shown that NFC is positively associated with higher self-efficacy (Rooij et al. (2017), https://doi.org/10.1080/13596748.2017.1381301, and Tan et al. (2020), https://doi.org/10.1007/s12528-019-09239-6), so we also expected NFC to be more strongly associated with the RPE subscale than with DP or EE.
And if the focus in burnout studies with teacher samples has been on the DP and EE subscales, it is all the more reason to also focus on the RPE subscale, especially because NFC was equally correlated with all MBI subscales in our teacher sample.
We had preregistered the exploratory analysis of the Demand-Resource-Ratio model with RPE in place of the MBI score, but this model did not have better fit indices than the initial model, which might be attributed to the evenly distributed associations between NFC and the subscales.
Furthermore, when constructing the exploratory model it became clear that NFC was indeed associated with RPE and EE via DRF and DTH, respectively, but the DP subscale did not have any meaningful paths within the model.
Since we have not preregistered any analysis of the association between NFC and DP or EE, and we do not have any theory-driven hypotheses regarding these associations, we would like to refrain from including these analyses in the paper in order not to report analyses that are less well-reasoned and not pre-registered.
A change that we will gladly implement is the more specific distinction between the terms "burnout" and "RPE subscale" in the manuscript, thank you for this advice.

@@

Although one can assume that Covid burden and years of experience are associated, there is a variety of factors that may also play a role.
Firstly, years of experience cannot be equated with age, as some teachers are lateral entry employees.
Secondly, age itself is not the only risk factor for Covid, but one of a long list of risk factors according to the Center for Disease Control and Prevention, such as disability, asthma, cancer, chronic heart disease, diabetes, HIV, weak immune function, obesity, mental disorders, pregnancy, physical inactivity, etc.
Since the item does not specify the kind of risk factor, there is no need to correct for any confound between Covid burden and years of experience.

@@

Thank you for this assessment.
It is true that the theoretical framework shifts within the manuscript.
This is motivated by the three different aims of the paper.
As the investigation of demands and resources in the context of Need for Cognition is very new, a smaller confirmatory model and a larger exploratory model likely contribute more to developing this approach than a highly complex and long paper with a theoretical framework that is still in its infancy.
The overarching framework in this manuscript is the role of Need for Cognition in burnout or burnout subscales, and depending on which specific aim the reader is interested in, they may skim over the others.
We have added subheadings to the introduction and expanded the last paragraph before the methods section to better convey these three aims:

@@

We are aware that the double-blind review process somewhat interferes with Open Science issues.
We learned how OSF projects can be anonymized only after submission of our manuscript.
We apologize that we did not give the reviewer the opportunity to check our preregistration/data/code.
Of course, we share our data and code openly on OSF and also provide a license for re-use (CC-4.0-BY).
The anonymized link is: https://osf.io/36ep9/?view_only=5169a1624e6d40c193bdc96121266ea9.

@@

Thank you for this suggestion.
The three-part-structure was exactly what we intended with this manuscript; a replication in a different sample, an analysis based on our own previous research, and an exploratory analysis to serve as a starting point for future research.
(As we have provided an answer to this issue in our response to your first comment, we would kindly refer to it here.)
